---
title: "National Geographic Research grant"
output: revealjs::revealjs_presentation
---

## Data Science in Agriculture Research

Data science plays a crucial role in enhancing agricultural practices by:

Precision Agriculture: Utilizing data from sensors and satellites to optimize crop yields and reduce waste.

Predictive Analytics: Analyzing historical data to forecast crop performance and pest outbreaks.

Soil Health Monitoring: Leveraging data to assess soil quality and recommend interventions.

Supply Chain Optimization: Enhancing logistics and distribution through data-driven insights.

## What is Data Science

-   Data science is an interdisciplinary field that uses scientific methods, processes, algorithms, and systems to extract knowledge and insights from structured and unstructured data.

## Slide with Plot

```{r}
library(ggplot2)

# Create a data frame with hypothetical data
data <- data.frame(
  Year = 2015:2021,  # Adjusted to match the length of Interest
  Interest = c(20, 30, 50, 70, 85, 90, 100)  # Hypothetical interest levels
)

# Create the line chart
ggplot(data, aes(x = Year, y = Interest)) +
  geom_line(color = "blue", size = 1.5) +
  geom_point(color = "red", size = 3) +
  labs(title = "Growth of Data Science Interest Over Years",
       x = "Year",
       y = "Interest Level") +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, 100, 10))
```

## Slide with R Code and Output

```{r, echo=FALSE}
library(ggplot2)

# Create a data frame with hypothetical data
data <- data.frame(
  Language = c("R", "Python"),
  Popularity = c(60, 90)  # Hypothetical popularity scores
)

# Create the plot
ggplot(data, aes(x = Language, y = Popularity, fill = Language)) +
  geom_bar(stat = "identity") +
  labs(title = "Popularity of R vs Python in Data Science",
       x = "Programming Language",
       y = "Popularity Score") +
  theme_minimal()
```
